Ricci-Ollivier Curvature of the Rooted Phylogenetic Subtree-Prune-Regraft Graph

### 2015-04-02 curvature.tex
might be good to actually updat the arXiv link before submission
changed a selects to moves to, removed doubled reference used to check arXiv fields

The automated computational analysis code can be found at \url{https://github.com/matsengrp/curvature}.
We omit most proofs which are unnecessary to understand the paper, and which can be found in~\cite{curvature_arxiv}.

@@

We first consider properties of the uniform \cuttable{(a.k.a.\ isotropic)} random walk on the rSPR graph.
Recall that the uniform random walk begins at a tree $T$ and selects a tree uniformly at random from $N(T)$.
\cuttable{We denote the coarse curvature of the uniform random walk between two trees $T$ and $S$ with $\curvature{T,S}$.}
Recall that \cuttable[the coarse uniform random walk curvature ]{}$\curvature{T, S} := 1 - \frac{W_1(m_T, m_S)}{d(T, S)}$.
For the uniform random walk, $m_T$ \cuttable[assigns]{is simply the probability measure assigning} a mass of $\frac{1}{\degree{T}}$ to each of $T$'s neighbors.
Our results follow from the lemmas of Section~\ref{sec:neighborhoods}.

>>>>

The automated computational analysis code can be found at \url{https://github.com/matsengrp/curvature}.
\cuttable[We omit most proofs which are unnecessary to understand the paper, and which can be found in~\cite{curvature_arxiv}.]{}

@@

We first consider properties of the uniform \cuttable{(a.k.a.\ isotropic)} random walk on the rSPR graph.
Recall that the uniform random walk begins at a tree $T$ and moves to a tree uniformly at random from $N(T)$.
\cuttable{We denote the coarse curvature of the uniform random walk between two trees $T$ and $S$ with $\curvature{T,S}$.}
Recall that \cuttable[the coarse uniform random walk curvature ]{}$\curvature{T, S} := 1 - \frac{W_1(m_T, m_S)}{d(T, S)}$.
For the uniform random walk, $m_T$ \cuttable[assigns]{is simply the probability measure assigning} a mass of $\frac{1}{\degree{T}}$ to each of $T$'s neighbors.
Our results follow from the lemmas of Section~\ref{sec:neighborhoods}.
